---
title: "How_to_use_Noir"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How_to_use_Noir}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  results = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Noir)
```
`Noir` allows you to pull information from a loaded FlowJo or SeqGeq workspace 
when connected via the FlowJoServer API. The FJServer plugin will need to be
started prior to starting this code. 


# Gather Loaded Workspace Names
## getWorkspaces()
This will make a call to the API and gather the name of loaded workspace. 
If no workspace is loaded it will return a waring message.
If the FJServer is not running it will return an error message.
You must open a previously saved workspace and begin the FlowJo Server plugin.

```{r getWorkspaces, eval = TRUE}
library(urltools)
library(httr)
library(jsonlite)

url <- "http://localhost:4567/api/v1/workspaces/all"
getWorkspaces(url)
```

# Create the Path To Samples From Loaded Workspace
## buildSamURL()
This will find the curretly loaded workspace and use that information to 
build the URL to find the names of samples loaded into the workspace
otherwise return an error message.
```{r buildSamURL, eval = FALSE}
library(urltools)
library(httr)
library(jsonlite)

url <- "http://localhost:4567/api/v1/samples/all?workspaceid="
urlSams <- buildSamURL(url)
```

# Gather Loaded Sample Names
## getSamples()
This will make a call to the API and gather the name of loaded samples. 
If no samples are loaded it will return a waring message.
```{r getSamples, eval = TRUE}
library(urltools)
library(httr)
library(jsonlite)

getSamples(urlSams)
```

# Create the Path To Parameters From Loaded Samples
## buildParamURL()
This will build the path to parameter based on currently loaded workspace
and samples. Otherwise will return a warning.
```{r buildParamURL, eval = FALSE}
library(urltools)
library(httr)
library(jsonlite)

url <- "http://localhost:4567/api/v1/parameters/all?workspaceid="
urlParams <- buildParamURL(url)
```

# Gather Parameters Associated With Loaded Samples
## getParameters()
This will make a call to the API and gather the name of loaded parameters. 
If no samples are loaded or no connection to API it will return a waring message.
```{r getParameters, eval = TRUE}
library(urltools)
library(httr)
library(jsonlite)

getParameters(urlParams)
```

# Create the Path To Populations From Loaded Workspace
## buildPopsURL()
This will build the path to populations based on currently loaded workspace
and samples. Otherwise will return a warning.
```{r buildPopsURL, eval = FALSE}
library(urltools)
library(httr)
library(jsonlite)

url <- "http://localhost:4567/api/v1/populations/all?workspaceid="
urlPops <- buildPopsURL(url)
```

# Gather Populations Associated With Loaded Samples
## getPopulations
This will make a call to the API and gather the name of sample populations. 
If no samples are loaded or no connection to API it will return a waring message.
```{r getPopulations, eval = TRUE}
library(urltools)
library(httr)
library(jsonlite)

getPopulations(urlPops)
```

